\begin{rubric}{Scientific career}

\entry*[2024 -- Present]%
	\textbf{Postdoctoral researcher, EMPA, Thun, Switzerland}
    \par Project: \emph{In-situ TEM tensile testing of crystalline-amorphous nanolayered materials}
    \par SNSF proposal: \emph{Grain boundary atomic scale mechanics in Ti (GRABIT)}
	\par Innosuisse Project: \emph{Quantized nanolaminates as industrial magnetron sputtering process}
	\par PI: \emph{Prof. Johann Michler, Dr. Xavier Maeder}

\entry*[2022 -- 2024]%
	\textbf{Postdoctoral researcher, Max-Planck Institut für Eisenforschung, Düsseldorf, Germany}
	\par DFG Project: \emph{Mechanical properties and hydrogen tolerance of particle-reinforced CCA produced by additive manufacturing}
	\par PI: \emph{Prof. Gerhard Dehm, Prof. Eric Jägle}

\entry*[2018 -- 2022]%
	\textbf{PhD, Max-Planck Institut für Eisenforschung, Düsseldorf, Germany}
    \par Advanced transmission electron microscopy group, Department of structure and nano-/ micromechanics of materials
	\par Thesis title: \emph{Microstructure and grain boundary evolution in titanium thin films.}
	\par Supervisor: \emph{Prof. Gerhard Dehm}, Group leader: \emph{Dr. Christian Liebscher}

\entry*[2016 -- 2018]%
	\textbf{M.Tech., Indian Institute of Technology, Madras, India}
	\par Metallurgical and materials engineering department
	\par Thesis title: \emph{Correlative microscopy of Magnesium - rare-earth alloys}.
    \par Thesis work performed as a \textbf{DAAD exchange program at Materials Chemistry, RWTH Aachen, Germany} with \emph{Prof. Jochen Schneider}
	\par Supervisors: \emph{Prof. B S Murty, Prof. K G Pradeep}
	
\entry*[2012 -- 2016]%
	\textbf{B.Tech., National Institute of Technology, Raipur, India} in Metallurgical engineering
    \par CGPA: 9.22/10 (Honours)
	
\end{rubric}