\makerubrichead{Positions of Responsibility}
\begin{itemize}
    \item[] \textbf{Supervision and teaching experience}
    \begin{enumerate}
        \item Supervised a Cambridge University summer intern for 8 weeks, 2023.
        \item Peer-reviewed a full-length journal article for \emph{Materialia}, 2023.
        \item Delivered a lecture on 'grain boundaries' as part of a seminar series at MPIE, 2021.
        \item Served as a teaching assistant under Prof. Ravi Shankar Kottada, IIT - Madras, 2016.
    \end{enumerate}    
    \item[] \textbf{Leadership \& Organization}
    \begin{enumerate}
        \item Member of European Microscopy Society (EMS) and Deutsche Gesellschaft für Elektronenmikroskopie e.V. (DGE), 2019-present.
        \item Internal PhD representative, 2019-2022.
        \item Member of MPIE's sustainability team, 2021-2023.
        \item Organized and participated in a teaching seminars and career planning seminar, 2021-2022.
        %\item Led a career planning seminar for PhD students, 2022.
        \item Managed MPIE's Twitter account, 2020-2023.
        \item Coordinated department weekly-seminars, 2022-23.
        \item Managed a high-vacuum furnace, 2021-2023.
    \end{enumerate}
    \item[] \textbf{Science communication}
    \begin{enumerate}
        \item Represented MPIE at the Bright World of Metals science slam event, 2023.
        \item Organized and spoke at "Pint of Science," Düsseldorf, 2021 and 2023.
        \item Represented MPIE at "Nacht-der-Wissenschaft (Science Night)," Düsseldorf, 2022.
        \item Attended the \textbf{Alexander-von-Humboldt scholarship-funded} Science Communication Summer School in Berlin, 2021, resulting in a published \textit{Declaration on the Future of Science Communication} presented to the German Parliament.
        \item Editorial team member for the Max-Planck PhD-net scientific magazine, "Offspring," 2019-2020.
    \end{enumerate}
\end{itemize}